---
title: "Assignment2-Rishi-Android"
author: "Ayush Rishi"
date: "2024-03-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Topic Description**

Android is my topic which is an operating system used in almost all the smart devices across the world. Here we have following details:

-   Link - <https://github.com/topics/android>

-   Repositories - We have total 115,766 public repositories.

-   Followers - We have total 146K followers.

-   Released Date - September 23, 2008

-   Filter Options - There are many filter options available such as Language, sort List of Required.

## Libraries for exceution

```{r}
library(httr)
library(jsonlite)
library(magrittr)
library(gh)
library(purrr)
library(dplyr)
library(knitr)
library(kableExtra)
library(lubridate)
library(ggplot2)
library(ggthemes)
library(tidyr)
```

## **Fetching 100 repos from Android**

```{r}
gitKey = "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"
Sys.setenv(GITHUB_PAT = gitKey)
response = gh("/search/repositories?q=topic:android",.limit = 100)
```

## **Table with columns name as full_name, created_at, size, language, topics in items sorted by size in descending order**

```{r}
df <- map_df(
  response$items,
  ~ tibble(
    full_name = .x$full_name,
    created_at = .x$created_at,
    size = .x$size,
    language = .x$language,
    topics = paste(.x$topics, collapse = ", ")
  )
) %>%
arrange(desc(size))

df <- slice(df, 1:10)
num_columns <- ncol(df)
column_width <- "4cm"
 
column_widths <- rep(column_width, num_columns)
kable(df, format = "html", 
      align = "c", caption = "Top 10 Repository sorted by size", escape = FALSE, row.names = FALSE) %>%
  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"), position = "center") %>%
  column_spec(column = 1:num_columns, width = column_widths)
```

## **Fetching 100 Owners details through login**

```{r}
repos <- response$items
Owner_Summary <- function(repos) {
  owner_login <- repos$owner$login
  owner_info <- gh("/users/{login}", login = owner_login)
  data.frame(
    login = owner_login,
    public_repos = owner_info$public_repos,
    created_at = owner_info$created_at,
    followers = owner_info$followers
  )
}
owners_data <- map_df(repos, Owner_Summary)
```

## **Table with columns name as login, public_repos(count), created_at(of the user), followers(count) in Owner sorted by public_repos in descending order**

```{r}
unique_owners_data <- owners_data %>%
  distinct(login, .keep_all = TRUE)

sorted_owners_data <- unique_owners_data %>%
  arrange(desc(public_repos)) %>%
  head(10)

kable(sorted_owners_data, format = "html", 
      align = "c", caption = "Top 10 Owners sorted by Public_repos", 
      col.names = c("login", "public_repos", "created_at", "followers"),
      escape = FALSE, 
      row.names = FALSE) %>%
  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"), position = "center")
```

## **Fetching 100 issues from Android**

```{r}
issue_data <- list()

# Iterate through the repositories and retrieve issue data
for (repo in response$items) {
  owner <- repo$owner$login
  repo_name <- repo$name
  
  
  # Retrieve issue data for the repository
  issues <- gh(paste0("/repos/", owner, "/", repo_name, "/issues"), state = "closed")
  if (length(issues) > 0) {
    most_recent_issue <- issues[[1]]
    title <- most_recent_issue$title
    created_at <- most_recent_issue$created_at
    closed_at <- most_recent_issue$closed_at
    days_to_close <- as.numeric(difftime(closed_at, created_at, units = "days"))
    issue_info <- data.frame(
      full_name = paste(owner, "/", repo_name),
      title = title,
      created_at = created_at,
      closed_at = closed_at,
      days_to_close <- as.integer(difftime(closed_at, created_at, units = "days"))
    )
    issue_data[[paste(owner, "/", repo_name)]] <- issue_info
  }
}
issue_data_df <- do.call(rbind, issue_data)
```

## **Table with columns name as full_name, title(of the issue), created_at, closed_at, days_to_close (the difference created_at and closed_at in days) for Issue sorted by days_to_close in ascending order**

```{r}
issue_data_df <- slice(issue_data_df, 1:10)

issue_data_df <- issue_data_df[order(issue_data_df$days_to_close), ]

kable(issue_data_df, format = "html", 
      align = "c", caption = "Top 10 Issue sorted Ascending by days_to_close", 
      col.names = c("full_name", "title", "created_at", "closed_at", "days_to_close"),
      escape = FALSE, 
      row.names = FALSE) %>%
  kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed", "responsive"), position = "center")
```

## **Bar Plot of top 5 other topics with respect to Android**

```{r}
item <- response$items
topics <- lapply(item, function(repo) repo$topics)

topics <- unlist(topics)
topics_freq <- table(topics)
sorted_topics_freq <- sort(topics_freq, decreasing = TRUE)

top_Topics_Occur <- names(sorted_topics_freq)[!grepl("^Android",names(sorted_topics_freq))][2:6]

data_Occur <- data.frame(
  topic = top_Topics_Occur,
  frequency = sorted_topics_freq[top_Topics_Occur]
)
data_Occur$frequency.Freq <- as.numeric(data_Occur$frequency.Freq)

ggplot(data_Occur, aes(x = reorder(topic, -frequency.Freq), y = frequency.Freq)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label=frequency.Freq), vjust=1.6, color="white", size=3.5)+
  labs(
    x = "Topic",
    y = "Frequency",
    title = "Top 5 Other Topics similar to 'Android'",
    subtitle = "Frequency Occurance",
  )  +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## **Above Bar Plot Description**

-   The above graph shows the 5 other topics that most frequently occur with the topic selected which is covid-19 and are sorted in descending order by frequency. Below are the name of 5 topics:

    -   **ios** - Frequency of occurrence is 35

    -   **java** - Frequency of occurrence is 17

    -   **cross-platform** - Frequency of occurrence is 12

    -   **javascript** - Frequency of occurrence is 12

    -   **Kotlin -** Frequency of occurrence is 12

## **Line Chart showing the trend of number of repos created each year**

```{r}
years <- sapply(response$items, function(repo) as.integer(substr(repo$created_at, 1, 4)))
year_counts <- data.frame(year = unlist(years))
min_year <- min(year_counts$year) 
max_year <- max(year_counts$year)  
all_years <- data.frame(year = min_year:max_year)
year_counts <- year_counts %>%
  complete(year = all_years$year) %>%
   group_by(year) %>%
  summarise(count = n())
y_breaks <- seq(0, max(year_counts$count), by = 8)
ggplot(year_counts, aes(x = year, y = count)) +
  geom_line() +
  geom_text(aes(label=count), vjust=1.6, color="black", size=3.5)+
  labs(
    title = "Number of Repositories Created Each Year",
    x = "Year",
    y = "Repository Count"
  ) +
  scale_x_continuous(breaks = unique(year_counts$year)) +
  scale_y_continuous(breaks = y_breaks)
```

## **Above Line Chart Description**

-   The above line shows the trend of the number of repos created each year

    -   **Year with Highest created Repo** - In **2016** 17 repos are created

    -   **Year with Lowest created Repo** - In **2023** only 1 repo is created

    -   **Information about other years** - In **2014** 15 repos and in **2017** 14 repos are created
